Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/5.Backend.tex
Chapter on Backend support done.

\subsection{Back-end Support}\label{chap:kokkosBackend}

@@

The implementation of the parallel\_for specific to the OpenMP execution space is shown in Figure~\ref{fig:KokkosExampleOMPBackEnd}. It shows the template argument of that class predefined to that execution space and shows how the~\emph{execute()} method calls the functor by calling ~\emph{exec\_range}. In can be seen that the Kokkos library relies on the back-end compiler to generate platform optimized, parallel code.

\begin{figure}
\begin{small}
\begin{Verbatim}[frame=leftline]
int main(int argc, char* argv[]) {
  Kokkos::initialize(argc,argv);
  {
    int N = atoi(argv[1]);
    Kokkos::View<int*> a("A", N);  
    Kokkos::parallel_for(
    Kokkos::RangePolicy<Kokkos::OpenMP>(N,
    [=](const int & i)
    {
      a(i)=i*i;
    }); 
  }
  Kokkos::finalize();
}
\end{Verbatim}
\end{small}
\caption{An application written in Kokkos shows the use of a~\emph{view}-type and parallel for loop.}
\label{fig:KokkosExample}
\end{figure}

@@

public:
  ...
  ... execute() const {(
  #pragma omp parallel num_threads(OpenMP::getPoolSize())
  {
    HostThreadTeamData& data=*(i->get_thread_data());
    ...
    range = data.get_work_partition();
    range(m_functor, range.first + m_policy.begin(),
    range.second + m_policy.begin());
  }
}

\end{Verbatim}
\end{small}
\caption{Library code giving an  insight into the impelemtnation of the OpenMP back-end shows ParallelFor class, its~\emph{execute} method and the internal use of the OpenMP pragma annotation.  internally gives an insight into the m maos how .}
\label{fig:KokkosExampleOMPBackEnd}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.3\textwidth]{img/Build.png}}
\caption{The compilation workflow includes the invocation of the platform compiler that is in charge to generate parallel   Building workflow}
\label{fig:workflow}
\end{figure}

>>>>

\section{Back-end Support}\label{chap:kokkosBackend}

@@

The implementation of the parallel\_for specific to the OpenMP execution space is shown in Figure~\ref{fig:KokkosExampleOMPBackEnd}. It shows the template argument of that class predefined to that execution space and shows how the~\emph{execute()} method calls the functor through ~\emph{exec\_range}. In can be seen that the Kokkos library relies on the back-end compiler to generate platform optimized, parallel code. For the OpenMP back-end implementation of the parallel for loop, OpenMP pragma annotations are used. Since the parallel for implies a barrier at the end of the parallel region, the return semantic of Kokkos::parallel\_for call is synchronous.

\begin{figure}
\begin{small}
\begin{Verbatim}[frame=leftline]
int main(int argc, char* argv[]) {
  Kokkos::initialize(argc,argv);
  {
    int N = atoi(argv[1]);
    Kokkos::View<int*> a("A", N);  
    Kokkos::parallel_for(
    Kokkos::RangePolicy<Kokkos::OpenMP>(N,
    [=](const int & i) {
      a(i)=i*i;
    }); 
  }
  Kokkos::finalize();
}
\end{Verbatim}
\end{small}
\caption{This example application written in Kokkos shows the use of a~\emph{view}-type and a parallel for loop. Both Kokkos types are templated to the OpenMP execution space.}
\label{fig:KokkosExample}
\end{figure}

@@

public:
  ...
  ... execute() const {(
#pragma omp parallel num_threads(OpenMP::gPoolSize())
  {
    HostThreadTeamData& data=*(i->get_thr_data());
    ...
    range = data.get_work_partition();
    range(m_functor, range.first + m_policy.begin(),
    range.second + m_policy.begin());
  }
}

\end{Verbatim}
\end{small}
\caption{This code shows the back-end implementation of a parallel loop in the Kokkos programing model. It shows a particular implementation of that generic pattern as a templated class to the OpenMP execution space. Also it shows the use of OpenMP pragma annotations that put platform compilers in charge to generate parallel code for the underlying hardware architecture.}
\label{fig:KokkosExampleOMPBackEnd}
\end{figure}

%\begin{figure}
%\centerline{\includegraphics[width=0.3\textwidth]{img/Build.png}}
%\caption{The compilation workflow includes the invocation of the platform compiler that is in charge to generate parallel   Building workflow}
%\label{fig:workflow}  
%\end{figure}
